Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2020-10-04 paper/paper.Rmd
Decided to rename the dataset to ptpl, for pteroglossus pluricinctus

# Methods
### Data collection/manipulation

>>>>

# Methods
## Seed dispersal simulation
the goal of this manuscript is to evaluate the effects of variation in animal movement and how these translate to seed dispersal distances. We developed an individual-based simulation in order to track single individuals or family groups in various tracking sessions and see how they disperse seeds.

  - What is the overall goal of this simulation?
  - What entails one simulation run
  - Overall description of how the simulation works
  - Variables that go into the simulation
  - Sources I used to reference: jones
2. Parameterization and source data
  - Data description
  - Gut retention time comes from previous literature and averages
  - Calculations at the different organizational levels
3. Evaluating fits?
4. Statistics associated to the simulations

### Data collection/manipulation
